Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-17 article/article.Rmd
Commit 2024-05-17 11:12

<!-- Aerosol change -->
The above clear sky reference values are not enough to describe the long term
variation due to the changes of the atmospheric constituents. As observed
by @Natsis2023, there is long term brightening effect, over Thessaloniki for the
studied period. In order to better describe this change, we used, estimations of AOD
change derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change
of $-3.8\,\%$ per year at AOD on $340$ nm, using a Brewer spectrophotometer. For 2005
to 2023, we derived the trend from the available AERONET data.

To create a unified trend for the long term change of the clear sky irradiance, we
sim simulated

>>>>

<!-- Aerosol change -->
The above clear sky reference values are not enough to describe the long term
variation due to the changes of the atmospheric constituents. As observed
by @Natsis2023, there is long term brightening effect, over Thessaloniki for the
studied period. In order to better describe this change, we used, estimations of AOD
change derived from two sources. For 1993 -- 2005, @Kazadzis2007 have found a change
of $-3.8\,\%$ per year at AOD on $340\,\text{nm}$, using a Brewer spectrophotometer. For 2005
to 2023, we derived the trend from the available AERONET data.

To create a unified trend for the long term change of the clear sky irradiance, we
simulated the values of AOD derived from those sources with Libradtran. For both, we
use the AOD at $500\,\text{nm}$, which was inferred by the available Ångström
exponent, and we choose the SZA of $55^\circ$ as a representative value for all runs.

For the period 1993 -- 2005

For the period 2005 -- 2005 we used
